A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-03-19 paper/paper.tex
adding indication on how to orient

More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as a base and gluing on top of it another copy lifted by one dimension. In the second copy, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on. In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by~$\kstar$.

@@

More generally, the standard $(n + 1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them on their border by a cylinder obtained as a third copy stretched in the new dimension. The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with $\kstar$.

>>>>

More generally, the standard augmented $(n + 1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as a base and gluing on top of it another copy lifted by one dimension. In the second copy, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on. In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by~$\kstar$. Note that the components may be oriented by letting each $n$-dimensional component point to the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ of the $n$-dimensional component with $0$.

@@

More generally, the standard $(n + 1)$-semi-cube can be obtained by taking two copies of the standard $n$-semi-cube serving as bottom and top face and connecting them on their border by a cylinder obtained as a third copy stretched in the new dimension. The bottom and top faces are obtained from the standard $n$-semi-cube by postfixing with respectively $L$ and $R$ while the cylinder is obtained by postfixing with $\kstar$. Note that the components can this time be oriented by letting each $n$-dimensional component go from the $(n-1)$-dimensional component obtained by replacing the leftmost $\kstar$ with $L$ to the one obtained by replacing the leftmost $\kstar$ with $R$.
